---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fdadata

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/bjoleary/fdadata/workflows/R-CMD-check/badge.svg)](https://github.com/bjoleary/fdadata/actions?query=workflow%3AR-CMD-check)
[![codecov](https://codecov.io/gh/bjoleary/fdadata/branch/main/graph/badge.svg?token=1AZQLVTB0B)](https://codecov.io/gh/bjoleary/fdadata)
[![lint](https://github.com/bjoleary/fdadata/workflows/lint/badge.svg)](https://github.com/bjoleary/fdadata/actions?query=workflow%3Alint)
<!-- badges: end -->

The goal of fdadata is to access public information from the [FDA website](https://www.fda.gov).

## Installation

<!-- You can install the released version of fdadata from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("fdadata") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bjoleary/fdadata")
```
## Example

Access FDA premarket data:

```{r example}
library(fdadata)
library(dplyr)

fdadata::premarket %>% 
  dplyr::sample_n(5) %>% 
  print()
```

Additional datasets include `fdadata::reglist`, `fdadata::pmn` (510(k)s and 
De Novos), `fdadata::pma`, and `fdadata::product_codes`. The registration and 
listing data can be joined into a single table using 
`fdadata::join_rl(fdadata::reglist)`. 

## Notes

This is a hobby project and is built on my own time. It is not from my employer 
and it is definitely not endorsed by my employer. For that matter, it’s not 
even endorsed by me. (Also, see the license for some important disclaimers.) 
The government ethics experts I checked in with told me that open sourcing a 
hobby project isn’t a problem though, so here we go.

They also said it was important that it is not intended for therapeutic use: 
So, don’t try to use this to make any health decisions or anything, okay? I’m 
not sure how you could, but I’m pretty sure anything you could come up with 
along those lines would be a pretty bad idea…
